\renewcommand*{\familydefault}{\sfdefault}
\documentclass[11pt]{book}
\parindent0pt
\parskip10pt

\title{\bf Nobility}
\author{Azriel Hoh}
\date{\today}

\begin{document}
\frontmatter
\maketitle
\tableofcontents
\chapter{Prologue}
Our mission is not easy. But then, has it ever been?

This time, it is to assassinate a veteran member of the Faction. In my clan, he is known as the \textit{The Skull} -- a title reflective of
the bandanna that covers his head. Trained in unarmed combat, he is notorious for the scars he leaves on the bodies of those who attempt to
harm him. By his hand, the final expression inscribed into their faces is always the same -- death. For no good reason, \textit{The Skull}
is not just his name, but an icon he had become.

% Write about the actual mission. The Skull separated us from each other. Lead this up to a cliff
Skull or no skull, at least he uses his head.

% Write about the scene that the protagonist sees - The Skull lands a hit that sends Ally into the air.
% TODO: rename Ally

Option one, complete the mission. End the chaos of injustice that we try so hard to eliminate. All that is needed is one clean slash, a
clear attack to force him past the edge of the cliff. Beyond that is certain death. Ally's last efforts were a perfect set up for this
opportunity of execution.

Option two, save Ally. This was the first time a stranger had been assigned such a critical role in a mission. But the choice was crucial.

To take a life, or save one. I have to choose. Now.

I leapt.

\mainmatter
\part{Discovery}
\chapter{Innocence}

\backmatter
\chapter{Epilogue}

\end{document}
